Binocular combination in the autonomic nervous system

### 2025-01-14 manuscript.Rmd
Added high resolution supplementary figure

Number of pages: 21

Number of figures: 4

Number of tables: 1

Number of words for abstract: 187/250

Number of words for introduction: 634/650

Number of words for discussion: 600/1500

Conflict of interest: The authors declare no competing financial interests.

Acknowledgements: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.

@@

@@

knitr::include_graphics(paste0(figdir,'SuppFig1.pdf'))

>>>>

@@

# Acknowledgements

Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.

# Declaration of interests

The authors declare no competing interests.

@@

knitr::include_graphics(paste0(figdir,'gamma_figure.pdf'))
